Sleep Quality Estimation using Accelerometer Data from Thigh-Mounted Devices During in Free Living Conditions

### 2023-03-21 presentation/index.qmd
create new ba plots

---
title: "Sleep Quality Estimation using Accelerometer Data from Thigh-Mounted Devices During in Free Living Conditions"
subtitle: "(working title)"
author: "Esben Lykke, PhD student"
date: "`r format(Sys.Date(), '%d %B, %Y')`"
format:
  revealjs:
    smaller: true
    theme: moon
    slide-number: true
    preview-links: auto
    logo: images/SDU_WHITE_RGB-png.png
    footer: https://github.com/esbenlykke/sleep_study
    css: my_styles.css
    scrollable: true
embed-resources: true
editor_options: 
  chunk_output_type: console
smooth-scroll: true
bibliography: references.bib
---

@@

```{r}
#| echo: false
library(gt)
library(arrow)
library(visNetwork)
library(tidymodels)
library(tidymodels)
```

- Sleep plays a vital role in health, thus, improving the assessment of sleep–wake outside of a laboratory environment is critical
- The gold standard (PSG) is costly and inconvenient.
- Methods for estimating sleep/wake based on accelerometry exist, primarily from wrist-worn devices
- Cole-Kripke and Sadeh algorithms are commonly used
- determine in-bed time is difficult, usually set by sleep log and/or human scorers
- detect wakefulness is difficult, worse performance in populations with sleep disorders
- typically a two level analysis: epoch based and summarized across night(s)
- Zmachine-derived sleep stats
-

Purpose...

@@

@@

::: {.fragment}

@@

```{r}
#| fig-asp: .4
multiclass_lps
```

@@

```{r}
#| fig-asp: .4
multiclass_tst
```

@@

## Results {transition="convex" .H2}

::: {.fragment .column width="50%"}

@@

::: {.fragment .column width="50%"}

@@

## ROC Curves {transition="convex"}

@@

## ROC Curves {transition="convex"}

@@

<!-- ## Lots of Metrics {transition="convex" .H2} -->

<!-- :::: {.columns} -->

<!-- ::: {.column} -->
<!-- ```{r} -->
<!-- source(here::here("presentation/code/tables_performance.R")) -->

<!-- tab1 -->
<!-- ``` -->
<!-- ::: -->

<!-- ::: {.column} -->
<!-- ```{r} -->
<!-- tab2 -->
<!-- ``` -->
<!-- ::: -->

<!-- :::: -->

>>>>

---
title: "Sleep Quality Estimation using Accelerometer Data from Thigh-Mounted Devices During in Free Living Conditions"
subtitle: "(working title)"
author: "Esben Lykke, PhD student"
date: "`r format(Sys.Date(), '%d %B, %Y')`"
format:
  revealjs:
    smaller: false
    theme: moon
    slide-number: true
    preview-links: auto
    logo: images/SDU_WHITE_RGB-png.png
    footer: https://github.com/esbenlykke/sleep_study
    css: my_styles.css
    scrollable: true
embed-resources: true
editor_options: 
  chunk_output_type: console
smooth-scroll: true
bibliography: references.bib
---

```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

# Background {transition="fade"}

@@

- Sleep plays a vital role in health, thus, improving the assessment of sleep–wake outside of a laboratory environment is critical
- The gold standard (PSG) is costly and inconvenient.
- Methods for estimating sleep/wake based on accelerometry exist, primarily from wrist-worn devices
- Cole-Kripke and Sadeh algorithms are commonly used
- determine in-bed time is difficult, usually set by sleep log and/or human scorers
- detect wakefulness is difficult, worse performance in populations with sleep disorders
- typically a two level analysis: epoch based and summarized across night(s)
- Zmachine-derived sleep stats
- Purpose...

@@

# Methods {transition="fade"}

@@

@@

```{r}
#| fig-asp: .4

multiclass_lps
```

@@

```{r}
#| fig-asp: .4

multiclass_tst
```
## Estimate Sleep Quality Metrics {transition="fade"}

```{r}
#| fig-asp: .4

br_ex
```

```{r}
#| fig-asp: .4
br_lps
```

```{r}
#| fig-asp: .4
br_tst
```

@@

# Results {transition="fade"}

## {.H2 transition="convex"}

:::: {.columns}
::: {.column width="50%"}

@@

::: {.column width="50%"}

@@

:::
::::

## Many ROC Curves {transition="convex"}

## {transition="convex"}

@@

## {transition="convex"}

@@

## Lots of Metrics {transition="convex"}

## {transition="convex"}
::: {layout="[[-1], [1], [-1]]"}
```{r}
source(here::here("presentation/code/tables_performance.R"))

tab_multi_metrics
```
:::

## {transition="convex" .H2}

::: {layout="[[-1], [1], [-1]]"}
```{r}
tab_crude_metrics
```
:::

## {transition="convex" .H2}

```{r}
tab_br_metrics
```
